manuscript - APP

### 2018-10-06 R/manuscript_app.Rmd
changes with manuscript revision

df_exp1b <- 
  readRDS(
    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk),
         ratio = (besselI(restk,0) * exp(targetk)) / (besselI(targetk,0) * exp(restk)),
         ratio_abs = abs(log((besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))),
         ratio_abs = abs(log(
           (besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))))
```

@@

```{r exp 2b - load data}
df_exp2b <- readRDS(here::here("..", "data", "exp2b", "responses", "responses_171023.rds")) %>% 
 filter(block != 0)

df_exp2b <- df_exp2b %>% mutate(restk = restk * 100, type = type * 100)

@@

df2_exp2b <- rbind(df_exp2b, df_exp2b)
df2_exp2b$version <- 2
df2_exp2b$version[1:nrow(df_exp2b)] <- 1

# this is a little hack, just to make a correct ggplot with one line
tmp <- df_exp2b$restk
df2_exp2b$restk[df2_exp2b$version == 2] <- df_exp2b$type
df2_exp2b$type[df2_exp2b$version == 2] <- tmp

df2_exp2b$version <- factor(df2_exp2b$version, labels = c("fix distractors' speed", "fix target's speed"))
```

@@

@@

p_sp05 <- plot_fig5(0.5)
p_sp1 <- plot_fig5(1)
p_sp2 <- plot_fig5(2)
p_sp4 <- plot_fig5(4)
p_sp8 <- plot_fig5(8)
p_sp8_legend <- plot_fig5(8, show_legend = T)

gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 3)
ggsave(file.path(plot_pth, "Fig5_sp05.eps"), p_sp05, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp1.eps"), p_sp1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp2.eps"), p_sp2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp4.eps"), p_sp4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp8.eps"), p_sp8, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp8_legend.eps"), p_sp8_legend, width = 6, height = 6)
# final plot was created in inkscape
```

@@

>>>>

df_exp1b <- 
  readRDS(
    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(tagetspd = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk),
         ratio = (besselI(restk,0) * exp(targetk)) / (besselI(targetk,0) * exp(restk)),
         ratio_abs = abs(log((besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))),
         ratio_abs = abs(log(
           (besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))))
```

@@

```{r exp 2b - load data}
df_exp2b <- 
  readRDS(
    file.path(data_pth, "exp2b", "responses", "responses_171023.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetspd = type, restspd = restk) %>% 
  mutate(id = factor(subject)) %>% 
  mutate(restspd = restspd * 100, targetspd = targetspd * 100) %>% 
  mutate(contrast_abs = abs(log2(targetspd / restspd)), 
         target_faster = (targetspd > restspd),
         ratio = (besselI(restspd,0) * exp(targetspd)) / (besselI(targetspd,0) * exp(restspd)),
         ratio_abs = abs(log((besselI(restspd,0) * exp(targetspd))) / (besselI(targetspd,0) * exp(restspd))),
         ratio_abs = abs(log((besselI(restspd,0) * exp(targetspd))) / (besselI(targetspd,0) * exp(restspd))))

@@

# df2_exp2b <- rbind(df_exp2b, df_exp2b)
# df2_exp2b$version <- 2
# df2_exp2b$version[1:nrow(df_exp2b)] <- 1
# 
# # this is a little hack, just to make a correct ggplot with one line
# tmp <- df_exp2b$restk
# df2_exp2b$restk[df2_exp2b$version == 2] <- df_exp2b$type
# df2_exp2b$type[df2_exp2b$version == 2] <- tmp
# 
# df2_exp2b$version <- factor(df2_exp2b$version, labels = c("fix distractors' speed", "fix target's speed"))
```

@@

## Descriptive statistics

```{r accuracy for speed differences }

df_exp2b %>% filter(abs(targetspd-restspd) >= 1) %>% summarize(m = mean(accuracy), sd = sd(accuracy)) %>% knitr::kable(digits = 2)

@@

p_sp05 <- plot_fig5b(0.5)
p_sp1 <- plot_fig5b(1)
p_sp2 <- plot_fig5b(2)
p_sp4 <- plot_fig5b(4)
p_sp8 <- plot_fig5b(8)
#p_sp8_legend <- plot_fig5(8, show_legend = T)

gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 3)
ggsave(file.path(plot_pth, "Fig5b_sp05.eps"), p_sp05, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5b_sp1.eps"), p_sp1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5b_sp2.eps"), p_sp2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5b_sp4.eps"), p_sp4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5b_sp8.eps"), p_sp8, width = 6, height = 6)

# final plot was created in inkscape
```

## Figure 6

```{r}

accu_summary <- df_exp2b %>% 
  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
  group_by(id, contrast_abs, contrast_abs_f, target_faster) %>% 
  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
  ungroup()
accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)

# duplicated values for contrast 0
accu_summaryx <- bind_rows(
  accu_summary,
  accu_summary %>% 
    filter(contrast_abs == 0, target_faster == F) %>% 
    mutate(target_faster = T)
)

p <- accu_summaryx %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_faster, shape = target_faster, linetype = target_faster)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5, linetype = "solid") +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
  theme(aspect.ratio = 1) + 
  scale_shape_discrete("Distractor type", labels = c("Faster then target", "Slower than target")) +
  scale_linetype_discrete("Distractor type", labels = c("Faster then target", "Slower than target")) +
  xlab("contrast") + ylab("Accuracy")
p
ggsave(file.path(plot_pth, "Figure6.png"), p, width = 9, height = 6)

@@

```{r exp2b - tests}
accu_summaryx %>%
  filter(contrast_abs!=0) %>% 
  group_by(contrast_abs) %>% 
  do(ez::ezANOVA(., dv = accu, wid = id, within = target_faster, detailed = T)$ANOVA) %>% 
  filter(Effect != "(Intercept)") %>% 
  mutate(p = round(p, 3), ges = round(ges,2), F = round(F,1)) %>% 
  transmute(`Contrast level` = contrast_abs, `F(1,15)`=F,p, ges) %>% 
  knitr::kable()
```
